### 2019-08-19 maciek.tex
Some fixes

The OPT places these three components in clusters $A, B$ and $D$, paying $2$ for migrating $a_3$ and $b_3$. The OPT has the freedom of choice of the cluster $D$ depending on the choices of the algorithm. We choose $D$ in such way that it does not contain neither $x$ nor $y$, and furthermore that the algorithm places any of nodes from $D$ at $x$'s or $y$'s place as the last possible move.
The configuration of OPT's clusters is then: $A$ contains $a_1, a_2,d_1$, $B$ contains $b_1, b_2,d_2$ and $D$ contains $a_3, b_3, d_3$.
Note that the requests between nodes of the same color are free for OPT, with the exception of nodes from $A$, $B$, and most notably $D$.

@@

At the begining, ALG has $\ell$ singleton-only components and each request increases their number by $1$.
Furthermore, before reaching either $d_1, d_2$ or $d_3$ in place of either $x$ or $y$, the algorithm must cycle through $\Omega(\ell)$ nodes from other clusters. This is guaranteed as the choice of $D$ can depend on the actions of the deterministic algorithm.
In total, OPT pays $2$, and ALG pays $\Omega(\ell)$ (for each request besides the first two).

>>>>

The OPT places these three components in clusters $A, B$ and $D$, paying $2$ for migrating $a_3$ and $b_3$. The OPT has the freedom of choice of the cluster $D$ depending on the choices of the algorithm. We choose $D$ in such way that it does not contain neither $x$ nor $y$, and furthermore that the algorithm places any of nodes from $D$ at $x$'s or $y$'s place as the last possible move \maciek{elaborate}.
The configuration of OPT's clusters is then: $A$ contains $a_1, a_2,d_1$, $B$ contains $b_1, b_2,d_2$ and $D$ contains $a_3, b_3, d_3$.
Note that the requests between nodes of the same color are free for OPT, with the exception of nodes from $A$, $B$, and most notably $D$.

@@

At the begining, ALG has $\ell$ singleton-only components and each request increases their number by $1$.
Furthermore, before reaching either $d_1, d_2$ or $d_3$ in place of either $x$ or $y$, the algorithm must cycle through $\Omega(\ell)$ nodes from other clusters. This can be guaranteed as the choice of $D$ can depend on the actions of the deterministic algorithm.
In total, OPT pays $2$, and ALG pays $\Omega(\ell)$ (for each request besides the first two).
